\tool: Programmable, Scalable, Efficient Secure Two-Party Computation

### 2017-10-24 OaklandSubmission/eval.tex
intro pass

The results for Na\"{i}ve Bayes are in Table~\ref{tab:nb}. As before, $d$ denotes the length of the input feature vector $x$ and $F$ is the number of possible values of $x_i$ for each $i \in [d]$.
Although, there are no multiplications in these benchmarks, these do have a significant number of comparisons (due to secret look-up) that result in many boolean-and gates (13k/750k denote 13000/75000). 
Here, again columns 4 and 5 show the results reported in~\cite{shafindss}. We observe that \tool generated code has competitive performance on this task. This improvement is significant as~\cite{shafindss} uses custom designed protocols and we are executing a generic two party computation (2PC). Moreover,~\cite{shafindss} remarks that generic 2PC did not scale to the smallest of their Naive Bayes classifiers and they had to scale down the prediction task and there a Yao-based implementation was 500 times slower. We have shown that by using \tool, generic 2PC can scale to real prediction tasks and provide performance competitive with specialized protocols.

>>>>

The results for Na\"{i}ve Bayes are in Table~\ref{tab:nb}. As before, $d$ denotes the length of the input feature vector $x$ and $F$ is the number of possible values of $x_i$ for each $i \in [d]$.
Although, there are no multiplications in these benchmarks, these do have a significant number of comparisons (due to secret look-up) that result in many boolean-and gates (13k/750k denote 13000/75000). 
Here, again columns 4 and 5 show the results reported in~\cite{shafindss}. We observe that \tool generated code has competitive performance on this task. This improvement is significant as~\cite{shafindss} uses custom designed protocols and we are executing a generic two party computation (2PC). Moreover,~\cite{shafindss} remarks that generic 2PC did not scale to the smallest of their Na\"{i}ve Bayes classifiers and they had to scale down the prediction task and there a Yao-based implementation was 500 times slower. We have shown that by using \tool, generic 2PC can scale to real prediction tasks and provide performance competitive with specialized protocols.
